---
title: Active Learning and Student Achievement - Experimental Analysis
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, fig.retina = 4)
```


```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(haven)
library(texreg)
library(estimatr)

# Parameters
stufac_file <- here::here("data", "all_appended.dta")
stu_file <- here::here("data", "stu_admin_all_latest.dta")
tpi_scores <- here::here("data", "tpi_scores.dta")
```


```{r}
# Read in data
df_stu <- 
  read_dta(stu_file) %>%
  left_join(read_dta("data/controls.dta") %>% select(stdid, ses, score), by = "stdid") %>% 
  transmute(
    stdid, 
    classid, 
    elite,
    ea_stud_group_criteria,
    z_active, z_activemath, z_activephysics,
    ses, score,
    female = gender - 1,
    age = 2017 - lubridate::year(b_birthdate),
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    b_ct_score_g1_z = if_else(grade == 2, b_ct_score, NA_real_) %>% scale() %>% as.vector(),
    b_ct_score_g3_z = if_else(grade == 4, b_ct_score, NA_real_) %>% scale() %>% as.vector(),
    b_ql_score_g1_z = if_else(grade == 2, b_ql_score, NA_real_) %>% scale() %>% as.vector(),
    b_ql_score_g3_z = if_else(grade == 4, b_ql_score, NA_real_) %>% scale() %>% as.vector(),
    b_rr_score_g1_z = if_else(grade == 2, b_rr_score, NA_real_) %>% scale() %>% as.vector(),
    b_rr_score_g3_z = if_else(grade == 4, b_rr_score, NA_real_) %>% scale() %>% as.vector(),
    e_ct_score_g1_z = if_else(grade == 2, e_ct_score, NA_real_) %>% scale() %>% as.vector(),
    e_ct_score_g3_z = if_else(grade == 4, e_ct_score, NA_real_) %>% scale() %>% as.vector(),
    e_ql_score_g1_z = if_else(grade == 2, e_ql_score, NA_real_) %>% scale() %>% as.vector(),
    e_ql_score_g3_z = if_else(grade == 4, e_ql_score, NA_real_) %>% scale() %>% as.vector(),
    e_rr_score_g1_z = if_else(grade == 2, e_rr_score, NA_real_) %>% scale() %>% as.vector(),
    e_rr_score_g3_z = if_else(grade == 4, e_rr_score, NA_real_) %>% scale() %>% as.vector(),
    b_math_score_g1_z = b_math_g1_score %>% scale() %>% as.vector(),
    b_math_score_g3_z = b_math_g3_score %>% scale() %>% as.vector(),
    e_math_score_g3_z = e_math_g3_score %>% scale() %>% as.vector(),
    b_physics_score_g1_z = b_physics_g1_score %>% scale() %>% as.vector(),
    b_physics_score_g3_z = b_physics_g3_score %>% scale() %>% as.vector(),
    e_physics_score_g3_z = e_physics_g3_score %>% scale() %>% as.vector()
  ) %>%
  filter(ea_stud_group_criteria == 2)

df <-
  read_dta(stufac_file) %>%
  distinct(stdid, course_name, facid, .keep_all = TRUE) %>% 
  inner_join(df_stu, by = "stdid") %>% 
  left_join(read_dta(tpi_scores), by = "facid") %>%
  mutate(
    classid_new = str_c(classid, course_name, sep = "_")
  )
```

\newpage


# Year 1 cohort

## Critical Thinking

```{r}
lm1 <-
  df %>%
  lm(e_ct_score_g1_z ~ z_activefac + b_ct_score_g1_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_ct_score_g1_z ~ z_activefac + b_ct_score_g1_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```

\newpage

## Quantitative Literacy

```{r}
lm1 <-
  df %>%
  lm(e_ql_score_g1_z ~ z_activefac + b_ql_score_g1_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_ql_score_g1_z ~ z_activefac + b_ql_score_g1_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


## Relational Reasoning

```{r}
lm1 <-
  df %>%
  lm(e_rr_score_g1_z ~ z_activefac + b_rr_score_g1_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_rr_score_g1_z ~ z_activefac + b_rr_score_g1_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


## Math

```{r}
lm1 <-
  df %>%
  lm(e_math_score_g3_z ~ z_activefac + b_math_score_g1_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_math_score_g3_z ~ z_activefac + b_math_score_g1_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


## Physics

```{r}
lm1 <-
  df %>%
  lm(e_physics_score_g3_z ~ z_activefac + b_physics_score_g1_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_physics_score_g3_z ~ z_activefac + b_physics_score_g1_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```

\newpage


# Year 3 cohort

## Critical Thinking

```{r}
lm1 <-
  df %>%
  lm(e_ct_score_g3_z ~ z_activefac + b_ct_score_g3_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_ct_score_g3_z ~ z_activefac + b_ct_score_g3_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


## Quantitative Literacy

```{r}
lm1 <-
  df %>%
  lm(e_ql_score_g3_z ~ z_activefac + b_ql_score_g3_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_ql_score_g3_z ~ z_activefac + b_ql_score_g3_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


## Relational Reasoning

```{r}
lm1 <-
  df %>%
  lm(e_rr_score_g3_z ~ z_activefac + b_rr_score_g3_z + classid_new, data = .)

lm2 <-
  df %>%
  lm(e_rr_score_g3_z ~ z_activefac + b_rr_score_g3_z + female + age + father_college + mother_college + ses + classid_new, data = .)


screenreg(list(lm1, lm2), groups = list("Treatment" = 1, "Control variables" = 2:7), custom.note = "%stars \n All models control for department-year-course fixed effects.", omit.coef = "classid", reorder.coef = c(2, 3, 4, 5, 6, 7, 8, 1), stars = c(0.01, 0.05, 0.1))
```


\newpage


# Functional forms

## Year 1

### Critical Thinking

```{r}
df %>% 
  ggplot(aes(z_activefac, e_ct_score_g1_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Quantitative Literacy

```{r}
df %>% 
  ggplot(aes(z_activefac, e_ql_score_g1_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Relational Reasoning

```{r}
df %>% 
  ggplot(aes(z_activefac, e_rr_score_g1_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Math

```{r}
df %>% 
  ggplot(aes(z_activefac, e_math_score_g3_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Physics

```{r}
df %>% 
  ggplot(aes(z_activefac, e_physics_score_g3_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


## Year 3

### Critical Thinking

```{r}
df %>% 
  ggplot(aes(z_activefac, e_ct_score_g3_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Quantitative Literacy

```{r}
df %>% 
  ggplot(aes(z_activefac, e_ql_score_g3_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```


### Relational Reasoning

```{r}
df %>% 
  ggplot(aes(z_activefac, e_rr_score_g3_z)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_smooth() +
  labs(
    caption = "All values reported in standard deviation units."
  )
```

